Badʾu-l-masīri fī taʾrīḫi-t-tafsīri--An Exploratory Data Analysis of 17 Tafāsīr From the Early 8th to the Late 14th

### 2016-12-16 tafaseer_group/03_results/Paper.Rmd

---
title: Badʾ al-masīr fī taʾrīḫ al-tafsīr--An Exploratory Data Analysis of 18 Tafasīr From the Early 8th to the Late 14th
 Century and Across a Wide Geographical Area Using Corpus Linguistical Methods
subtitle: Universities of Leipzig and Maryland
author: 'Franziska Blunck, Sarosh Bukhari, Dr. Maryam Foradi, Thomas Davis Keppen, Jonathan Raphael Schmid, BA; supervising: Dr. Matthew Thomas Miller and Dr. Maxim Romanov'
date: "`r format(Sys.time(), '%d %B %Y')`"
tags: [tafsir, tafseer, tafasir, tafaseer, quran, exegesis, corpus linguistics, exploratory data analysis]
abstract: Through web scraping, a large corpus of *tafsīr* (Quran exegetical work) was downloaded and initial exploratory data analysis was performed on it using by identifying number of words written by the different authors on each chunk or passage, as well as on each *sūra* (chapter of the Quran). Subsequently, with the help of network analysis, it was possible to draw first conclusions about the acquired data.
output: pdf_document
toc: no
fontsize: 12pt
geometry: margin=1.5in
lang: en
documentclass: article
latex_engine: xelatex
urlcolor: blue
---

@@

How has Islamic interpretation of the Quran changed over time? Have certain sections of the Quran enjoyed more attention from religious scholars and if so, has preference shifted with time? Does geographic distance equate to divergent preference for scholars who are contemporaneous to one another? Is doctrinal affiliation the primary factor in a *mufassir* (Islamic exegete) giving a section of the Quran more consideration? To answer these questions, we sought out exegetical works that were in a manageable and navigable digital format. As part of an effort to make Islamic scholarship more accessible, the Jordanian-based *Royal Aal al-Bayt Institute for Islamic Thought* commissioned the creation of [altafsir.com](altafsir.com), an online repository of classical works of *tafsīr*. The format of the website allows a user to select a specific *āya* (verse from the Quran) and see the relevant section of *tafsīr* that provides commentary on the *āya*. This structure, along with the fact that the texts are typed in and not photos of scanned pages, made the website ideal for our research which required that the texts be in a digital format and segmented according to the verse that is being commented on. The ultimate goal of [altafsir.com](altafsir.com) is to provide a diverse collection of texts that are derived from various traditions, sects, and schools of jurisprudence. That desired breadth has yet to be achieved. The website currently has seventeen complete tafasīr that were all written by *sunnī* (one of the major two sects of Islam) scholars.

@@

When we sorted the verses from most written about to least, we observed some suspicious patterns. Consecutive verses were appearing next to one another on the list and they had identical word counts. When we inspected the files in our corpus, we found that there were duplicate chunks of text. The problem was that most of the writers alternated between writing about singles verses and writing about groups of consecutive verses that dealt with a single narrative or theme. If a section of a *tafsīr* covered consecutive verses together, [altafsir.com](altafsir.com) repeated that segment of text when each of those verses were selected on the website. When the script to download the tafasīr was run, it downloaded the repeated segments of texts and organized them as if they were unique to a single verse. Only three of the writers in the corpus consistently wrote about single verses and therefore did not succumb to the duplicate text problem. Of the 87 *tafsīr* works listed on the website, 69 turned out to be completely empty and one author, *Ibn ʿArafa*, only provided commentary on *sūratān*. Both were removed from the corpus used for analysis, which consequently consists of 17 works comprising $i_{total}=16444304$ words.

We ran a script that looked for duplicate texts and removed any repeated segments. Since we were not able to get word counts for specific verses, we decided to focus on the *sūra* or chapters of the Quran. There is a huge range of *sūra* lengths, with *sūrat al-baqara*, the longest, consisting of 286 verses and *sūrat al-kawṯar*, the shortest, consisting of 3 verses, so looking at how long the commentary was for a specific *sūra* relative to total *tafsīr* length would probably just leave us with something that resembles a list of *sūra*, from longest to shortest. We chose instead to look at length of *tafsīr* commentary divided by the length of the *sūra* it is commenting. We looked at the top twenty-five *sūrāt* for each *mufassir* and observed that the number of shared *sūra* among the writers of the corpus ranged from twelve to twenty-two. The relationship between the *mufassirūn* was visualized using [Gephi](https://gephi.org/), a free/open-source program used for social network analysis.

## 1.1 The Groupings

@@

1. *Ibnu-l-Ǧauzī*, *at-Tabarī*, *Ibn Kaṯīr*, *Ibn ʿAṭīya*, and *al-Baġawī*
2. *az-Zamaḫšarī*, *al-Baiḍāwī*, and *an-Nasafī*
3. *ar-Rāzī*, *al-Fayrūzabādī*, *al-Qurṭubī*, *al-Khāzin*, and *Abū Ḥayyān*
4. *al-Maḥallī* and *as-Suyūṭī*, *as-Samarqandī*, *al-Māwardī*, and *Ibn ʿAbdu-s-Salām*

TODO: disambiguate mufassir names wherever they end up appearing first. Here's the unclear ones (mails from Dec 15): There is more than one al-Razi and Ibn atiyah.  Our al-Razi is Fakhr al-Din and our ibn atiya is ibn atiya al-andalusi. And al- khazin is Ala' al-din al-khazin.

# 1 The corpus
## 1.1 Data origin and possible intentions behind its compilation
## 1.2 Data extraction and transformation into processable outer form
## 1.3 Authors of the 18 works
### 1.3.1 d. 728: Jarir ibn Atiyah (Yamamah, Damascus)
### 1.3.2 d. 925: Muhammad ibn Zakariya al-Razi (Rey)
### 1.3.3 d. 923: Al-Tabari (Amol-Baghdad)
### 1.3.4 d. 971: Abū Ja'far al-Khāzin (Iran?)
### 1.3.5 d. 1044: Al-Baghawi (?)
### 1.3.6 d. 1058: Al-Mawardi (Basrah-Baghdad)
### 1.3.7 d. 1142: Abu Hafs Umar an-Nasafi (Nakhshab-Samarqand)
### 1.3.8 d. 1144: Al-Zamakhshari (Kwharezm-Mecca-Khwarezm)
### 1.3.9 d. 1201: Ibn al-Jawzi (Baghdad)
### 1.3.10 d. 1261: Ibn 'Abd as-Salam (Damascus-Egypt)
### 1.3.11 d. 1273: Al-Qurtubi (Cortoba)
### 1.3.12 d. 1286: Al-Baydawi (Shiraz-Tabriz)
### 1.3.13 d. 1310: Shams al-Dīn al-Samarqandī (Samarqand)
### 1.3.14 d. 1401: Ibn Arafa (Tunis)
### 1.3.15 d. 1414: Fairuzabadi (Fars-Mekka)
### 1.3.16 d. 1505: Al-Suyuti (Cairo)
### 1.3.17 d. 1344: Abu Hayyan al-Gharnati (Spain-Cairo)
### 1.3.18 d. 1373: Ibn Kathir (Bosra-Damascus)
# 1.4 Conventional categorisation and inter-relationships of the authors
# 2 Analysis
# 2.1 Most frequent words (MFW), Zipf's law
# 2.2 Stylometrics
# 2.3 Topic Modelling results
# 2.4 Congruences of observations with conventional views
# 2.5 Notable differences to conventional views
# 3 Conclusion
# 3.1 Possible theses based on findings
# 3.2 Discussion of necessary further work
# 4 Bibliography

>>>>

---
title: Badʾu-l-masīri fī taʾrīḫi-t-tafsīri--An Exploratory Data Analysis of 17 Tafāsīr From the Early 8th to the Late 14th
 Century and Across a Wide Geographical Area Using Corpus Linguistical Methods
subtitle: Universities of Leipzig and Maryland
author: 'Franziska Blunck, Sarosh Bukhari, Dr. Maryam Foradi, Thomas Davis Keppen, Jonathan Raphael Schmid, BA; supervising: Dr. Matthew Thomas Miller and Dr. Maxim Romanov'
date: "`r format(Sys.time(), '%d %B %Y')`"
tags: [tafsir, tafseer, tafasir, tafaseer, quran, exegesis, corpus linguistics, exploratory data analysis]
abstract: Through web scraping, a large corpus of *tafsīr* (Quran exegetical work) was downloaded and initial exploratory data analysis was performed on it by identifying the number of words written by the different authors on each chunk or passage, as well as on each *sūra* (chapter of the Quran). Subsequently, with the help of network analysis, it was possible to draw first conclusions about the acquired data.
output: pdf_document
toc: no
fontsize: 12pt
geometry: margin=1.5in
lang: en
documentclass: article
latex_engine: xelatex
urlcolor: blue
---

@@

How has Islamic interpretation of the Quran changed over time? Have certain sections of the Quran enjoyed more attention from religious scholars and if so, has preference shifted with time? Does geographic distance equate to divergent preference for scholars who are contemporaneous to one another? Is doctrinal affiliation the primary factor in a *mufassir* (Islamic exegete) giving a section of the Quran more consideration? To answer these questions, we sought out exegetical works that were in a manageable and navigable digital format.

# 2 The corpus

As part of an effort to make Islamic scholarship more accessible, the Jordanian-based *Royal Aal al-Bayt Institute for Islamic Thought* commissioned the creation of [altafsir.com](altafsir.com), an online repository of classical works of *tafsīr*. The format of the website allows a user to select a specific *āya* (verse from the Quran) and see the relevant section of *tafsīr* that provides commentary on the *āya*. This structure, along with the fact that the texts are typed in and not photos of scanned pages, made the website ideal for our research which required that the texts be in a digital format and segmented according to the verse that is being commented on. The ultimate goal of [altafsir.com](altafsir.com) is to provide a diverse collection of texts that are derived from various traditions, sects, and schools of jurisprudence. That desired breadth has yet to be achieved. The website currently has seventeen complete tafāsīr that were all written by *sunnī* (one of the major two sects of Islam) scholars.

# 3 Exploratory data analysis

@@

When we sorted the verses from most written about to least, we observed some suspicious patterns. Consecutive verses were appearing next to one another on the list and they had identical word counts. When we inspected the files in our corpus, we found that there were duplicate chunks of text. The problem was that most of the writers alternated between writing about singles verses and writing about groups of consecutive verses that dealt with a single narrative or theme. If a section of a *tafsīr* covered consecutive verses together, [altafsir.com](altafsir.com) repeated that segment of text when each of those verses were selected on the website. When the script to download the tafāsīr was run, it downloaded the repeated segments of texts and organized them as if they were unique to a single verse. Only three of the writers in the corpus consistently wrote about single verses and therefore did not succumb to the duplicate text problem. Of the 87 *tafsīr* works listed on the website, 69 turned out to be completely empty and one author, *Ibn ʿArafa*, only provided commentary on *sūratān*. Both were removed from the corpus used for analysis, which consequently consists of 17 works comprising $i_{total}=16444304$ words.

We ran a script that looked for duplicate texts and removed any repeated segments. Since we were not able to get word counts for specific verses, we decided to focus on the *sūra* or chapters of the Quran. There is a huge range of *sūra* lengths, with *sūrat al-baqara*, the longest, consisting of 286 verses and *sūrat al-kawṯar*, the shortest, consisting of 3 verses, so looking at how long the commentary was for a specific *sūra* relative to total *tafsīr* length would probably just leave us with something that resembles a list of *sūra*, from longest to shortest. We chose instead to look at length of *tafsīr* commentary divided by the length of the *sūra* it is commenting. We looked at the top twenty-five *suwar* for each *mufassir* and observed that the number of shared *sūra* among the writers of the corpus ranged from twelve to twenty-two. The relationship between the *mufassirūn* was visualized using [Gephi](https://gephi.org/), a free/open-source program used for social network analysis.

## 3.1 The Groupings

@@

1. *Ibnu-l-Ǧawzī*, *aṭ-Ṭabarī*, *Ibn Kaṯīr*, *Ibn ʿAṭīya*, and *al-Baġawī*
2. *az-Zamaḫšarī*, *al-Bayḍāwī*, and *an-Nasafī*
3. *ar-Rāzī*, *al-Fayrūzābādī*, *al-Qurṭubī*, *al-Ḫāzin*, and *Abū Ḥayyān*
4. *al-Maḥallī* and *as-Suyūṭī*, *as-Samarqandī*, *al-Māwardī*, and *Ibn ʿAbdi-s-Salām*

# 4 Bibliography

Blah blah blah

# Appendix

TODO: disambiguate mufassir names wherever they end up appearing first. Here's the unclear ones (mails from Dec 15): "There is more than one al-Razi and Ibn atiyah.  Our al-Razi is Fakhr al-Din and our ibn atiya is ibn atiya al-andalusi. And al- khazin is Ala' al-din al-khazin."

TODO: remove below draft headings before handing the paper in!

## 1.1 Data origin and possible intentions behind its compilation
## 1.2 Data extraction and transformation into processable outer form
## 1.3 Authors of the 18 works
### 1.3.1 d. 728: Jarir ibn Atiyah (Yamamah, Damascus)
### 1.3.2 d. 925: Muhammad ibn Zakariya al-Razi (Rey)
### 1.3.3 d. 923: Al-Tabari (Amol-Baghdad)
### 1.3.4 d. 971: Abū Ja'far al-Khāzin (Iran?)
### 1.3.5 d. 1044: Al-Baghawi (?)
### 1.3.6 d. 1058: Al-Mawardi (Basrah-Baghdad)
### 1.3.7 d. 1142: Abu Hafs Umar an-Nasafi (Nakhshab-Samarqand)
### 1.3.8 d. 1144: Al-Zamakhshari (Kwharezm-Mecca-Khwarezm)
### 1.3.9 d. 1201: Ibn al-Jawzi (Baghdad)
### 1.3.10 d. 1261: Ibn 'Abd as-Salam (Damascus-Egypt)
### 1.3.11 d. 1273: Al-Qurtubi (Cortoba)
### 1.3.12 d. 1286: Al-Baydawi (Shiraz-Tabriz)
### 1.3.13 d. 1310: Shams al-Dīn al-Samarqandī (Samarqand)
### 1.3.14 d. 1401: Ibn Arafa (Tunis)
### 1.3.15 d. 1414: Fairuzabadi (Fars-Mekka)
### 1.3.16 d. 1505: Al-Suyuti (Cairo)
### 1.3.17 d. 1344: Abu Hayyan al-Gharnati (Spain-Cairo)
### 1.3.18 d. 1373: Ibn Kathir (Bosra-Damascus)
# 1.4 Conventional categorisation and inter-relationships of the authors
# 2 Analysis
# 2.1 Most frequent words (MFW), Zipf's law
# 2.2 Stylometrics
# 2.3 Topic Modelling results
# 2.4 Congruences of observations with conventional views
# 2.5 Notable differences to conventional views
# 3 Conclusion
# 3.1 Possible theses based on findings
# 3.2 Discussion of necessary further work
